---
title: "Find analysis"
author: "Gordana"
date: "`r Sys.Date()`"
output: html_document
---


```{r message=FALSE, warning=FALSE}
library(mice)
library(emmeans)
library(tidyverse)
library(glmmTMB)
library(DHARMa)
library(table1)
library(gridExtra)
library(naniar)
```

## Data

### Missing data

```{r}
load(file = "../../data/for_impute.Rdata")

VIM::aggr(for_impute, numbers=TRUE, sortVars=TRUE,cex.axis = .7, prop = FALSE,
          combined = TRUE, labels=names(for_impute),
          oma = c(8,3,2,4))


```
```{r}
for_little <- for_impute %>% 
  select(Indigeneous.Status,RacialCat,Search.Reason,Age.of.Contact,Sex,
         X003.VEHICLE,VEHICLE_CHECK,PERSON_CHECK,Year,Operation_Type,
         PACKAGE_or_THING,Contacting.Member.Rank)

mcar_test(for_little)
```


### Table 2 - Data summary

```{r}

load(file = "../../data/imputed_20_mids")

# full data
full_data <- complete(mids_data, action = 0)  %>% 
  select(Found, Age.of.Contact, Sex, RacialCat, Search.Reason, Reporting.Station,
         Operation_Type) 


write.csv(full_data, file = "../../data/full_data.csv", row.names = FALSE)

Table1 <- table1( ~ Age.of.Contact + Sex + RacialCat +
         Search.Reason + Operation_Type, data = full_data)
Table1
write.csv(Table1, file = "../results/Table1.csv", row.names = FALSE)

```


### Table 3 - Find rates by racial appearence



```{r}
dis_ratios <- full_data %>% 
  group_by(RacialCat, Found) %>% 
  summarise(n = n()) %>% 
  pivot_wider(names_from = Found, values_from = n) %>% 
  mutate(Found = `TRUE`,
         Total = (`TRUE` + `FALSE`),
         find_rate = Found / Total) %>% 
  select(RacialCat, Total, Found, find_rate)

dis_ratios$dis_ratio = dis_ratios$find_rate/dis_ratios$find_rate[dis_ratios$RacialCat == "CAUCASIAN"][1]

dis_ratios <- dis_ratios %>% 
  as.data.frame() %>% 
  arrange(as.character(RacialCat), .by_group = TRUE)

dis_ratios
```

### Figure 1 a - Find rates by operation type


```{r}
full_data %>% 
  group_by(Operation_Type, Found) %>% 
  summarise(n = n()) %>% 
  pivot_wider(names_from = Found, values_from = n) %>% 
  mutate(find_rate = `TRUE` / (`TRUE` + `FALSE`)) 
```

## Analysis

### Primary - Racial Appearence



#### Imputed data analysis

```{r}

# this code takes ~ 10 minutes, so i have saved the fitted model
# vic_imputed <- with(data = mids_data,
#                  exp = glmmTMB(Found ~ Age.of.Contact  + Sex + RacialCat + Search.Reason +
#                                (1|Reporting.Station), 
#                                family = binomial,
#                                control=glmmTMBControl(optimizer=optim,
#                                                       optArgs=list(method="BFGS"))))
# 
# 
# 
# 
# save(vic_imputed,file = "../results/vic_imputed")
load(file = "../results/vic_imputed")

OT_em_imp <- emmeans(vic_imputed, ~ RacialCat)
OT_em_log_imp <- regrid(OT_em_imp, "log")
cont_OT_imp = contrast(OT_em_log_imp, "trt.vs.ctrl",type = "response",
                   exclude = c("LATIN AMERICAN","OTHER","MEDITERRANEAN","INDIAN SUBCONTINENTAL"))

imp_result = bind_cols(confint(cont_OT_imp), p.value = summary(cont_OT_imp)$p.value) %>% 
    as.data.frame() %>% 
  mutate(data = "imputed data")

imp_result
```


```{r}
imp_result %>% 
  transmute(contrast,
            perc_dec = round((1-ratio)*100),
            perc_dec_lower = round((1-asymp.UCL)*100),
            perc_dec_upper = round((1-asymp.LCL)*100))
```



#### Complete case analysis

```{r}

# extract complete cases
complete.cases <- complete(mids_data, action = 0)  %>% 
  select(Found, Age.of.Contact, Sex, RacialCat, Search.Reason, Reporting.Station,
         Operation_Type) %>% 
  na.omit()

# fit model to complete cases
vic_complete <- glmmTMB(Found ~ Age.of.Contact  + Sex + RacialCat + Search.Reason +
                      (1|Reporting.Station), 
                      data = complete.cases,
                      family = binomial,
                      control=glmmTMBControl(optimizer=optim,
                                             optArgs=list(method="BFGS")))

# check residuals 
simulationOutput <- simulateResiduals(fittedModel = vic_complete , plot = F)
res <- residuals(simulationOutput, quantileFunction = qnorm, outlierValues = c(-7,7))
scatter.smooth(res ~ predict(vic_complete, re.form = NA))

```

Calculate relative risks and confidence intervals

```{r}
OT_em <- emmeans(vic_complete, ~ RacialCat)
OT_em_log <- regrid(OT_em, "log")
cont_OT = contrast(OT_em_log, "trt.vs.ctrl",type = "response",
                   exclude = c("LATIN AMERICAN","OTHER","MEDITERRANEAN","INDIAN SUBCONTINENTAL"))


comp_result = bind_cols(confint(cont_OT), p.value = summary(cont_OT)$p.value) %>% 
    as.data.frame() %>% 
  mutate(data = "complete cases")

comp_result

```

#### Plot

Here I create several plots and then stitch them all into one below


```{r}
p = position_dodge(width=0.6)


# Plot of confidence intervals
CI_plot <- bind_rows(comp_result, imp_result) %>% 
  ggplot(aes(y = contrast, group = data)) + 
  geom_vline(xintercept = 1) +
  geom_point(aes(x=ratio, shape=data), size=2, position = p) +
  geom_linerange(aes(xmin=asymp.LCL, xmax=asymp.UCL, lty = data ), position = p) +
  coord_cartesian(ylim=c(1,5), xlim=c(0.58, 1.25))+
  annotate("text", x = 0.85, y = 4.8, label = "less items found", size = 3) +
  annotate("text", x = 1.15, y = 4.8, label = "more items found", size = 3) +
  xlab("disproportionality ratio")+
  theme_classic() +
  theme(legend.position = "none")+ 
  theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

# CI_plot 



combined_results <- bind_rows(imp_result, comp_result) %>% 
  mutate(p.value = ifelse(p.value < 0.001, "<0.001", format(round(p.value,3), nsmall = 3)),
         ratio = round(ratio, 2),
         conf.low = format(round(asymp.LCL,2), nsmall = 2),
         conf.high = format(round(asymp.UCL,2), nsmall = 2),
         contrast = str_to_title(contrast, locale = "en")) %>% 
  select(data, contrast, ratio, conf.low, conf.high, p.value) %>%
  mutate(estimate_lab = paste0(ratio, " (", conf.low, "-", conf.high, ")")) %>% 
  bind_rows(
    data.frame(
      data = "Data",
      contrast = "Racial Appearence",
      p.value = "p-value",
      estimate_lab = "Disproportionality ratio (95% CI)"
    )
  ) %>% 
  mutate(model = fct_rev(fct_relevel(data, "Data"))) 


p_left <- 
  combined_results  %>% 
  ggplot(aes(y = contrast, group = data))+
  geom_text(aes(x = 0, label = contrast), hjust = 0, fontface = "bold")+
  geom_text(
    aes(x = 0.9, label = estimate_lab),
    hjust = 1,
    fontface = ifelse(combined_results$estimate_lab == "Disproportionality ratio (95% CI)", "bold", "plain"), 
    position = p
  )+
  theme_void() +
  coord_cartesian(xlim = c(0, 0.9))
# p_left


p_right <-
  combined_results  %>% 
  ggplot() +
  geom_text(
    aes(x = 0, y = contrast, group = data, label = p.value),
    hjust = 0,
    fontface = ifelse(combined_results$p.value == "p-value", "bold", "plain"), 
    position = p
  ) +
  theme_void() +
  xlim(-0.2,0.3)

 # p_right
 
 
 p_data <-
  combined_results  %>% 
  ggplot() +
  geom_text(
    aes(x = 0, y = contrast, group = data, label = data),
    hjust = 1,
    position = p,
    fontface = ifelse(combined_results$data == "Data", "bold", "plain"), 
  ) +
  theme_void() +
   xlim(-1,0.2)

 # p_data
```


Combined plot 

```{r, fig.height=3.5, fig.width=10}
library(patchwork)
# final plot arrangement
p_left + CI_plot + p_right + p_data + plot_layout(ncol = 4, widths = c(4.3,3,1,1.5))

ggsave(filename = "../results/dis_ratio_plot.tiff", width = 10, height = 3.5)
```





## Methods

All analyses were conducted in R version 4.0.3.

## Data 

We classified racial appearance ….
We combined "ABORIGINAL","BOTH TSI & ABORIGINAL","TORRES STRAIT ISLANDER (TSI)" into "ABORIGINAL and/or TSI" and coded "NO INFO PROVIDED", "NOT STATED / UNKNOWN" as Missing
Unknown sex was coded to Missing
Recruit (small numbers) combined into Const
Coded search reason by combining to weapons, drugs and graffiti
We combined finding package or thing due to small numbers
We truncated age at 80
Find is any of PROHIBITED.WEAPONS, DANGEROUS.ARTICLES, ,CONTROLLED.WEAPONS,.ARTICLES,GRAFFITI.IMPLEMENTS, VOLATILE.SUBSTANCES.TYPES
We removed any with SEARCH_WARRANT or DPCSA_S_81_SRCH_WITH_WARRANT, as well as Person.Reports = No Person data

There was a large amount of missing data in the model variables, with Racial Appearance having 3404 (18%) missing values, search reason having 998 (5%) missing values, and Age and Sex less than 1% missing (Figure XX attached).  





